The pollination trade-off

### 2019-04-09 paper/manuscript.Rmd
Number of words in main text and abstract together in same line

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)
# library(magrittr)
# library(foreach)
# library(drake)
# # load functions
# f <- lapply(list.files("../code", full.names = T), source)
```

```{r draft-details}
drake::loadd(msc_wordcount, abs_wordcount)
```

**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx. `r format(round(msc_wordcount$n_words_stri/10)*10, big.mark = ",")` words (excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` min. reading time.

**Abstract length:** `r abs_wordcount$n_words_stri` words.

>>>>

**Number of words:** `r readd(abs_wordcount)$n_words_stri` in the abstract; `r format(round(readd(msc_wordcount)$n_words_stri/10)*10, big.mark = ",")` in the main text.

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)
# library(magrittr)
# library(foreach)
# library(drake)
# # load functions
# f <- lapply(list.files("../code", full.names = T), source)
```
```
